\chapter{Results}
\label{results}
In this chapter, we investigate the performance of the resulting software.

KamehaMail is fully functional and implements almost all of the intended features. Additionally, we test the scalability of the searching capabilities of the interface on large amount of e-mails.

\section{Benchmark setup}
First of all, we prepared an environment sufficient for testing. Enron e-mail data set\cite{klimt2004enron} is a collection of roughly half million e-mails, freely accessible for anyone. Using the implemented admin interface, we dropped and indexed the Enron e-mails into one mailbox in the database. The e-mails were tagged according to the original position in the folder.

We measured the results on two data sets of different sizes to provide better overview of performance scaling.

The first data set consists of almost 27.000 e-mails found in the mailbox of the Enron user V. Kaminski. The second data set consists of 200.000 e-mails selected randomly from multiple mailboxes. The full data set was not benchmarked because of resource limitations.

On both data sets, we measured the space needed for their storing in the database, and the time required to complete several testing queries.

\section{Benchmark results}
The results obtained on the indexed data sets are reported in \autoref{table:bench}.

As expected, the more complicated cases were tested, the longer it took ElasticSearch to give the results. Increases in response time were caused by more complex queries, more indexed e-mails and more returned results. On the other hand, from the perspective of the user, the 7.4-times increase in the amount of data did not have a significant impact on the response time of the search. 

The indexing process itself scaled satisfactorily --- indexing performance was approximately 40 e-mails per second on average, and it varied only negligibly with the increase of the index e-mail count.
\begin{table}[t]
\centering
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{p{10em} l l}
 \toprule
Query & 26.675 e-mails & 200.000 e-mails\\
\midrule
\texttt{tag:inbox} & &\\
\hline
Top 10 results & 1ms & 5ms\\
Top 50 results & 3ms & 8ms\\
Top 100 results & 8ms & 11ms\\
\hline
\texttt{tag:inbox and approval}  & &\\
\hline
Top 10 results & 14ms & 48ms\\
Top 50 results & 16ms & 68ms\\
Top 100 results & -- & 70ms\\
\hline
\texttt{tag:inbox and approval and time:<1.1.2002}  & &\\
\hline
Top 10 results & 18ms & 52ms\\
Top 50 results & 20ms & 59ms\\
Top 100 results & -- & 57ms\\
\hline
 & &\\
\hline
E-mail files disk space & 417MB & 2.7GB\\
ElasticSearch's index disk space & 112MB & 394MB\\
\bottomrule
\end{tabular}
\caption{Search and space results from benchmark performed on Enron e-mail data set.}
\label{table:bench}
\end{table}